Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-02-04 paper/main.tex
paper full

\myparagraph{Comparison of the best solutions found}
%
We now turn our analysis to the best (minimum) fitness found at the end of the
run by the two best algorithms, that is, \CEGOinv and UMM$_{400}$. We show in
Table~\ref{tab:results} the mean fitness (and standard deviation) of the best
solution found over the 10 runs of each algorithm, together with a 95\%
confidence interval (CI) around their mean fitness difference. 
Except for PFSP
instances \texttt{rec05} and \texttt{rec31}, the differences are statistically
significant in favour of \CEGOinv (the intervals do not contain the value
zero). Nevertheless, the CIs indicate that the differences, although
consistent, are relatively small.
The detailed results of UMM$_{100}$  and UMM$_{200}$  and the original \CEGOorig are given in Table~\ref{tab:results_fit}. In this table, it can be seen that the quality of \CEGOorig  solutions is similar to the UMM$_{100}$ version of UMM.

@@

Table~\ref{tab:results} shows a brief comparison of time and the full ones are given in Table~\ref{tab:time}. The difference is time in impressive. 
The average runtime for all the instances is around 0.3 minutes, 1.15 minutes and 4.5 minutes respectively for the  versions with 100, 200 and 400 fitness evaluations. 
For CEGO in both versions the average time for 400 evaluations is more than 22 hour. This is 300 times slower than UMM for the same number of function evaluations. 
Moreover, UMM scales good for larger instances in quality performance. 
The computational complexity of UMM is $O(n \log n)$ at each iteration which causes the abrupt differencein the time performance of the algorithms. The details can be seen in Table~\ref{tab:results_time}.

>>>>

\myparagraph{Comparison of the best solutions found}
%
We now turn our analysis to the best (minimum) fitness found at the end of the
run by the two best algorithms, that is, \CEGOinv and UMM$_{400}$. We show in
Table~\ref{tab:results} the mean fitness (and standard deviation) of the best
solution found over the 10 runs of each algorithm, together with a 95\%
confidence interval (CI) around their mean fitness difference. 
Except for PFSP
instances \texttt{rec05} and \texttt{rec31}, the differences are statistically
significant in favour of \CEGOinv (the intervals do not contain the value
zero). Nevertheless, the CIs indicate that the differences, although
consistent, are relatively small.
The detailed results of UMM$_{100}$  and UMM$_{200}$  and the original \CEGOorig are given in Table~\ref{tab:results_fitness}. In this table, it can be seen that the quality of \CEGOorig  solutions is similar to the UMM$_{100}$ version of UMM.

@@

Table~\ref{tab:results} shows a brief comparison of time and the full ones are given in Table~\ref{tab:results_time}. The difference is time in impressive. 
The average runtime for all the instances is around 0.3 minutes, 1.15 minutes and 4.5 minutes respectively for the  versions with 100, 200 and 400 fitness evaluations. 
For CEGO in both versions the average time for 400 evaluations is more than 22 hour. This is 300 times slower than UMM for the same number of function evaluations. 
Moreover, UMM scales good for larger instances in quality performance. 
The computational complexity of UMM is $O(n \log n)$ at each iteration which causes the abrupt difference in the time performance of the algorithms. The details can be seen in Table~\ref{tab:results_time}.
